---
title: "Plant growth"
author: "Dulki Nihinsa"
date: "2025-09-09"
output: html_document
---

# Introduction

The PlantGrowth dataset is a built-in dataset in R that contains the weights of plants under three conditions: a control group (ctrl), and two treatment groups (trt1, trt2).

This report explores the dataset, summarizes the plant growth for each group, and compares them visually.

# Results

```{r}
head(PlantGrowth)
```

```{r}
str(PlantGrowth)
```

## Mean for each group

```{r}
mean(subset(PlantGrowth, group == "ctrl")$weight)
```

```{r}
mean(subset(PlantGrowth, group == "trt1")$weight)
```

```{r}
mean(subset(PlantGrowth, group == "trt2")$weight)
```

## Median for each group

```{r}
median(subset(PlantGrowth, group == "ctrl")$weight)
```

```{r}
median(subset(PlantGrowth, group == "trt1")$weight)
```

```{r}
median(subset(PlantGrowth, group == "trt2")$weight)
```

## Including Plots

```{r}
boxplot(weight ~ group, data = PlantGrowth,
        main = "Plant Growth by Treatment Group",
        xlab = "Group",
        ylab = "Weight",
        col = c("lightblue", "lightgreen", "lightpink"))
```

# Conclusion

From the analysis, the differences in mean and median plant weights across the three groups can be observed. The boxplot provides a clear visual comparison, suggesting that treatment conditions may influence plant growth compared to the control.

```{r}
sessionInfo()
```

